Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
edits

{\em The first approach} uses a {\em naive}
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a {\em completeness threshold}, i.e.,
the number of iterations required to sufficiently unwind
the closed-loop state-space system such
that the boundaries are not violated for any larger number of iterations.
As it requires explicit unfolding up to the completeness
threshold, this approach may result in state space explosion.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state space one. 
  Such a representation allows to study the  input-to-state dynamics, whereas
  transfer functions only represent input-output relations and are not sufficient 
  to ensure deeper properties, e.g. safety.
%
\item We proposes a synthesis of state feedback controllers that,
  in addition to the already existing stability conditions,
  ensures safety properties,
  which is only  possible in the state-space representation. 
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modelling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

>>>>

{\em The first approach} uses a {\em naive}
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a {\em completeness threshold}, i.e.,
the number of iterations required to sufficiently unwind
the closed-loop state-space system such
that the boundaries are not violated for any larger number of iterations.
As it requires explicit unfolding up to the completeness
threshold, this approach may suffer from state space explosion.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state space one. 
  Such a representation allows to study the  input-to-state dynamics, whereas
  transfer functions only represent input-output relations and are not sufficient 
  to ensure deeper properties, e.g. safety.
%
\item We propose a synthesis of state feedback controllers that,
  in addition to the already existing stability conditions,
  ensures safety properties,
  which is only  possible in the state-space representation. 
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modelling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}
